---
title: "Exploring Whisky: The Journey to My Next Bottle of Scotch"
subtitle: "Part 4: Review Text Analysis"
author: "Ben Greenwald"
output: html_document
---

# TO-DO
* add items.

---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, 
#                      results = "show", cache = FALSE, autodep = FALSE)
#knitr::opts_knit$set(root.dir = "external-data/whisky")
```

```{r, include=FALSE}
#here::i_am("analysis/scotch-analysis-part4.R")
#source(here::here("analysis", "scotch-analysis-part4.R"))
```

## Part 4: Review Text Analysis
Add introduction. 

## Project Goals
As a reminder, the overarching goals of this mutli-part project are threefold:

* To augment my learning about whisky brands, regions, flavors, and options
* To understand the breadth, depth, and quirks of the scotch whisky industry
* To leverage data to determine which whiskies I ought to try myself

## Review Text Analysis
* text analysis of review description content
* variables of interest: description
* Q: do flavor notes emerge overall? by brand? by type?
* Q: what descriptive words are used commonly to describe scotch?
* sentiment analysis
* groupings of interest: author
* Q: how does sentiment vary across review authors?
* Q: does preference for types or brands vary across review authors?
* Q: with which authors do my tastes align?

https://www.tidytextmining.com/preface.html

## Conclusions
Add conclusions. 

## Next Steps
Add next steps.